### 2018-07-15 Sections/quality_of_service.tex
Ent purification fin

More concretely, we distribute two Bell pairs of fidelity $F$ between Alice and Bob. Let us assume a bit-flip error model in this instance\footnote{The same protocol can be employed to correct against phase-flip errors by operating in a Hadamard-rotated basis.}, in which case the imperfect Bell pairs are of the form,
\begin{align}
\hat\rho^F_{A,B} &= F\ket{\Phi^+}\bra{\Phi^+} + (1-F)\hat{X}_1\ket{\Phi^+}\bra{\Phi^+}\hat{X}_1 \nonumber \\
&= F\ket{\Phi^+}\bra{\Phi^+} + (1-F)\ket{\Psi^+}\bra{\Psi^+},
\end{align}
That is, we have a mixture of,
\begin{align}
\ket{\Phi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{0}_B + \ket{1}_A\ket{1}_B),	
\end{align}
with probability $F$, and,
\begin{align}
\ket{\Psi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{1}_B + \ket{1}_A\ket{0}_B),	
\end{align}
with probability \mbox{$1-F$}. The goal is to `filter' out the latter of these.

Alice and Bob then perform their entanglement purification protocol -- operations to reduce them to a single Bell pair of higher fidelity,
\begin{align}
\mathcal{E}_\text{purif}(\hat\rho^{F_\text{in}}_{A,B} \otimes \hat\rho^{F_\text{in}}_{A,B}) \to \hat\rho^{F_\text{out}}_{A,B},
\end{align}
where,
\begin{align}
F_\text{out}>F_\text{in}.
\end{align}

The purification process $\mathcal{E}_\text{purif}$ is realised very simply by Alice and Bob both performing parity measurements\index{Bell measurement} on their two qubits, whose measurement outcomes indicate whether the two qubits were equal ($+$) or different ($-$) -- their parity. These are easily implemented using CNOT gates, using the construction shown in Fig.~\ref{fig:parity_meas}. They complete the protocol by classically communicating their measurement outcomes, and performing appropriate local corrections.

@@

\paragraph{No errors}

Suppose there was no error. Then the input state was,
\begin{align}
\ket\psi_\text{in} &= \ket{\Phi^+}\bra{\Phi^+} \otimes \ket{\Phi^+}\bra{\Phi^+}\\
&= \frac{1}{2}(\ket{0}_1\ket{0}_2+\ket{1}_1\ket{1}_2)(\ket{0}_3\ket{0}_4+\ket{1}_3\ket{1}_4).\nonumber
\end{align}
Now upon inspection it is evident that if a parity projection between Alice's two qubits (1 and 3) yields the $+$ outcome, Bob's projection (2 and 4) must also yield $+$. Similarly, for the $-$ outcome. Upon classically communicating that they measured consistent outcomes, they are satisfied the final state is error-free, and it is, leaving them with a perfect $\ket{\Phi^+}$ state.

\paragraph{One error}

Now suppose there was a bit-flip error on the first qubit of the first pair. Now the input state is,
\begin{align}
\ket\psi_\text{in} &= \hat{X}_1 \ket{\Phi^+}\bra{\Phi^+}\hat{X}_1 \otimes \ket{\Phi^+}\bra{\Phi^+}\\
&= \frac{1}{2}(\ket{1}_1\ket{0}_2+\ket{0}_1\ket{1}_2)(\ket{0}_3\ket{0}_4+\ket{1}_3\ket{1}_4).\nonumber
\end{align}
Upon performing the parity measurements as before, suppose Alice measures the $+$ outcome. Now Bob must measure the $-$ outcome, and a comparison of measurement outcomes diagnoses this single bit-flip error, which may subsequently be corrected with an additional bit-flip.

\paragraph{Two errors}

In the above two scenarios (no error, or exactly one error), the state is correctable to a perfect Bell pair. What if there are two errors? Consider the input state with bit-flips affecting both Bell pairs. Then,
\begin{align}
\ket\psi_\text{in} &= \hat{X}_1 \ket{\Phi^+}\bra{\Phi^+}\hat{X}_1 \otimes \hat{X}_3\ket{\Phi^+}\bra{\Phi^+}\hat{X}_3\\
&= \frac{1}{2}(\ket{1}_1\ket{0}_2+\ket{0}_1\ket{1}_2)(\ket{1}_3\ket{0}_4+\ket{0}_3\ket{1}_4).\nonumber
\end{align}
Upon performing the parity measurement, both Alice and Bob are guaranteed to measure the same outcome, as per the error-free case. However this isn't error-free at all since the remaining state is $\ket{\Psi^+}$ not $\ket{\Phi^+}$. That is, the bit-flip error has permeated through to the `corrected' state.

Following this example it is evident that our rudimentary entanglement purification protocol can correct at most one bit-flip error. For this reason a mixed state is only correctable if \mbox{$F>1/2$} to begin with. Otherwise errors are more likely to permeate than be corrected, thereby reducing output fidelity.

>>>>

More concretely, we distribute two Bell pairs of fidelity $F$ between Alice and Bob. Let us assume a bit-flip error model in this instance\footnote{The same protocol can be employed to correct against phase-flip errors by operating in a Hadamard-rotated basis.}, in which case the imperfect Bell pairs are of the form,
\begin{align}
\hat\rho^F_{A,B} &= F\ket{\Phi^+}\bra{\Phi^+} + (1-F)\hat{X}_1\ket{\Phi^+}\bra{\Phi^+}\hat{X}_1 \nonumber \\
&= F\ket{\Phi^+}\bra{\Phi^+} + (1-F)\ket{\Psi^+}\bra{\Psi^+},
\end{align}
That is, we have a mixture of,
\begin{align}
\ket{\Phi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{0}_B + \ket{1}_A\ket{1}_B),	
\end{align}
with probability $F$, and,
\begin{align}
\ket{\Psi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{1}_B + \ket{1}_A\ket{0}_B),	
\end{align}
with probability \mbox{$1-F$}. The goal is to `filter' out the latter of these.
x 
Alice and Bob then perform their entanglement purification protocol -- operations to reduce them to a single Bell pair of higher fidelity,
\begin{align}
\mathcal{E}_\text{purif}(\hat\rho^{F_\text{in}}_{A,B} \otimes \hat\rho^{F_\text{in}}_{A,B}) \to \hat\rho^{F_\text{out}}_{A,B},
\end{align}
where,
\begin{align}
F_\text{out}>F_\text{in}.
\end{align}

The purification process $\mathcal{E}_\text{purif}$ is realised very simply by Alice and Bob both performing parity measurements\index{Bell measurement} on their two qubits, whose measurement outcomes indicate whether the two qubits were equal ($+$) or different ($-$) -- their parity. These are easily implemented using CNOT gates, using the construction shown in Fig.~\ref{fig:parity_meas}, which implement the projectors,
\begin{align}\index{Parity measurement}\index{Parity projectors}
\hat\Pi^+ &= \ket{0,0}\bra{0,0} + \ket{1,1}\bra{1,1}, \nonumber \\
\hat\Pi^- &= \ket{0,1}\bra{0,1} + \ket{1,0}\bra{1,0}.
\end{align}

They complete the protocol by classically communicating their measurement outcomes, and performing appropriate local corrections.

@@

Suppose there were no errors, the ideal case. Then the input state was,
\begin{align}
\ket\psi_\text{in} &= \ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4}\\
&= \frac{1}{2}(\ket{0}_1\ket{0}_2+\ket{1}_1\ket{1}_2)(\ket{0}_3\ket{0}_4+\ket{1}_3\ket{1}_4).\nonumber
\end{align}
Upon parity measurement we obtain,
\begin{align}
\hat\Pi^+_{1,3} \ket{\Phi^+}_{1,2}\ket{\Phi^+}_{3,4} &= \ket{\Phi^+}_{2,4},\nonumber \\
\hat\Pi^-_{1,3} \ket{\Phi^+}_{1,2}\ket{\Phi^+}_{3,4} &= \hat{X}_2\ket{\Phi^+}_{2,4},
\end{align}
and we obtain the desired output Bell-pair (with an $\hat{X}$ correction in the case of the odd-parity outcome).

Note that if both qubits from one Bell-pair are subject to bit-flips, this is equivalent to no error, since,
\begin{align}
	\hat{X}_1\hat{X}_2\ket{\Phi^+}_{1,2}=\ket{\Phi^+}_{1,2}.
\end{align}

Now suppose there was a bit-flip error on the first qubit of the first pair. Now the input state is,
\begin{align}
\ket\psi_\text{in} &= \hat{X}_1 \ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4}\\
&= \frac{1}{2}(\ket{1}_1\ket{0}_2+\ket{0}_1\ket{1}_2)(\ket{0}_3\ket{0}_4+\ket{1}_3\ket{1}_4).\nonumber
\end{align}
Now upon parity measurement we obtain,
\begin{align}
\hat\Pi^+_{1,3} \hat{X}_1\ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4} &= \hat{X}_2\ket{\Phi^+}_{2,4},\nonumber \\
\hat\Pi^-_{1,3} \hat{X}_1\ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4} &= \ket{\Phi^+}_{2,4},
\end{align}
and following correction we achieve a bit-flipped Bell-pair.

Finally, with both Bell-pairs subject to a single bit-flip,
\begin{align}
\ket\psi_\text{in} &= \hat{X}_1\hat{X}_3 \ket{\Phi^+}_{1,2}\ket{\Phi^+}_{3,4} \\
&= \frac{1}{2}(\ket{1}_1\ket{0}_2+\ket{0}_1\ket{1}_2)(\ket{1}_3\ket{0}_4+\ket{0}_3\ket{1}_4).\nonumber
\end{align}
Upon performing the parity measurement,
\begin{align}
\hat\Pi^+_{1,3} \hat{X}_1\hat{X}_3\ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4} &= \ket{\Phi^+}_{2,4},\nonumber \\
\hat\Pi^-_{1,3} \hat{X}_1\hat{X}_3\ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4} &= \hat{X}_2\ket{\Phi^+}_{2,4},
\end{align}
recovering the expected Bell-pair, without an erroneous bit-flip.

Evidently, the output Bell-pair is subject to an unexpected bit-flip iff one of the Bell-pairs was subject to a bit-flip error. This yields the output fidelity,
\begin{align}
F_\mathrm{out} = \frac{{F_\mathrm{in}}^2}{{F_\mathrm{in}}^2 + (1-F_\mathrm{in})^2},
\end{align}
and thus the purification protocol improves fidelity provided that \mbox{$F_\mathrm{in}>1/2$}.
